\chapter*{Acknowledgments}
\addcontentsline{toc}{chapter}{Acknowledgments}

It is such an intense period, the Ph.D. You go from one extreme to another very quickly. If at the start of the week you are excited about an idea, it not unusual to be frustrated by the end of it, when the results are revealed. You become humbler, but also more confident; you learn so much and even so you realize that there will always something new to discover. It is also a period to meet brilliant people, to entice your creativity, and to discover yourself and your limits.

I am in profound debt with Jacques-Olivier Lachaud and Hugues Talbot for their generosity and their support, surpassing on several occasions their duties as supervisors. I particularly admire the frankness of Jaco in our discussions and the kindness of Hugues. I am very proud to have both of you as my supervisors.

I am honored to have Yuri Boykov, Isabelle Debled-Rennesson and Olivier Lézoray as reviewers of this manuscript. I am very thankful for the time they dedicated to the reading of this work and their valuable remarks. I am pleased with the acceptance of Simon Masnou and Nelly Pustelnik to be part of the jury.

I would not have been writing these words if I have not crossed with inspiring people in my path. I express my gratitude to Luziane Ferreira de Mendonça, which introduced me to optimization modelling and image processing; to Luis Peñaranda, who encouraged me to pursue a master's program in France; and to Nabil Mustafa to have sparkled in me an interest on research.

These last four years would have been tougher without the friendship of Mauricio and Thayane; the soirées with Carlos, Uğur and Pedro; the enlightening discussions with Evgeny, Monika and Bruno; the laughs at lunchtime with Hasti, Gizem, Bastien, Clement and Lars. The astonishing beauty of the Savoie region and the lake of Bourget were defintely a source of inspiration. I would like to thank the hospitality I found at ESIEE Paris and the "bonne ambiance" among the members of Lama at Université Savoie Mont Blanc, in particular Céline Acary-Robert.

I thank my family for their continuous support and to have made me feel less lonely, even being so far away from them. Finally, I would not have endured this period without the comprehension, the wise words, and the love of Sailon.